---
title: "COMPARE FEATURE TRANSFORMATION"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{COMPARE_FEATURE_TRANSFORMATION}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# TL;DR (Too Long; Didn’t Read)

## Log Transformer

- Helps with skewness
- No predetermined range for scaled data
- Useful only on non-zero, non-negative data

## Min-Max Scaler

- Rescales to predetermined range [0–1]
- Doesn’t change distribution’s center (doesn’t correct skewness)
- Sensitive to outliers

## Max Abs Scaler

- Rescales to predetermined range [-1–1]
- Doesn’t change distribution’s center
- Sensitive to outliers

## Standard Scaler

- Shifts distribution’s mean to 0 & unit variance
- No predetermined range
- Best to use on data that is approximately normally distributed

## Robust Scaler

- 0 mean & unit variance
- Use of quartile ranges makes this less sensitive to (a few) outliers
- No predetermined range

## Power Transformer

- Helps correct skewness
- 0 mean & unit variance
- No predetermined range
- Yeo-Johnson or Box-Cox
- Box-Cox can only be used on non-negative data

SOURCE: https://medium.com/@sjacks/feature-transformation-21282d1a3215

# ILLUSTRATION

## Log Transformer

$$ X' = log(X) $$

## Min-Max Scaler

$$ X' = \frac{X - X{min}}{X{max} - X{min}} $$

## Max Absolute Scaler

$$ X' = \frac{X}{max(abs(X))} $$

## Standard Scaler

$$ X' = \frac{X - \mu}{\sigma}  $$

## Robust Scaler

$$ X' = \frac{X - Q_1(X)}{Q_3(X) - Q_1(X)}$$

- Q1: the 1st quartile (25th quantile) and Q3: the 3rd quartile (75th quantile)

## Power Transformer

$$ x(\lambda) = \{^{\frac{x^\lambda - 1}{\lambda}, \space if \space \lambda \ne 0 }_{log(x), \space if \space \lambda = 0}  $$

## Data using

```{r}
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(bestNormalize)

df <- scorecard::germancredit

df <- df %>% 
  mutate(amt__original = credit.amount,
         amt_log = log(credit.amount),
         amt_min_max = (credit.amount - min(credit.amount))/(max(credit.amount) - min(credit.amount)),
         amt_max_abs = credit.amount / max(abs(credit.amount)),
         amt_standard = (credit.amount - mean(credit.amount)) / sd(credit.amount),
         amt_robust = (credit.amount - quantile(credit.amount, 1/4)) / (quantile(credit.amount, 3/4) - quantile(credit.amount, 1/4)),
         amt_power = bestNormalize(credit.amount) %>% predict()
         )

```

```{r, warning=FALSE, fig.height=7, fig.width=7}
p <- df %>% 
  select(starts_with("amt")) %>% 
  tidyr::pivot_longer(cols = starts_with("amt")) %>% 
  ggplot(aes(x = value, fill = name, color = name))+
  geom_histogram()+
  scale_color_ipsum() +
  scale_fill_ipsum() +
  facet_wrap(~name, scales = "free", ncol = 3)+
    labs(title = "Compare feature transformation",
       x = NULL,
       y = NULL)+
  theme_ipsum_ps(grid="XY", axis="xy") +
  theme(legend.position="none")
  
p  
```
